---
title: "Marketing Intelligence Individual Assignment"
author: "Stavros Tsentemeidis"
date: "6/27/2019"
output:
  prettydoc::html_pretty:
    theme: leonids
  github_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Repository    
The whole project is under this repository at my GitHub account or at the second link referring to my personal website.       
**https://github.com/stsentemeidis/House_Prices_Seattle**   


### Loading the files | Performing Calculations
</br>
At this point we run the **main_script.R**, which is the main script of the project responsible to running all the necessary *calculations, transformations and results* for the final report.   

```{r main, echo=FALSE, warning = FALSE, results='hide'}
source('main_script.R')
```


## Explanation & summary of the dataset

To begin with let's have a look at the meaning of the initial variables provided for the dataset.     

*   **id**: a notation for a house   
*   **date**: date house was sold   
*   **price**: price is prediction target   
*   **bedrooms**: number of bedrooms per house   
*   **bathrooms**: number of bathrooms per house     
*   **sqft_living**: square footage of the home   
*   **sqft_lot**: square footage of the lot        
*   **floors**: total floors (levels) in house     
*   **waterfront**: house which has a view to a waterfront    
*   **view**: has been viewed     
*   **condition**: how good the condition is (overall)    
*   **grade**: overall grade given to the housing unit, based on King County grading system  


From the below summary and description we can see that:    

1. There are no **missing values**, so our dataset is complete.
2. The variables *condition* and *grade*  are ordinal variables.
3. The variables above need to be converted from int to *factors*.
4. *Bedrooms*, *bathrooms* and *floors* are variables with discrete levels that can be converted to factors probably later on.. 


```{r summary, echo=FALSE, warning = FALSE}
kable(summary(df_train))%>%
  kable_styling(bootstrap_options = "striped", font_size = 11)%>%
  scroll_box(width = "100%", height = "400px")
```


```{r Correlation 1, echo=FALSE, warning = FALSE, fig.align='center', fig.width = 8, fig.height= 7}
plot_correlation(numeric_data_train, size_p = 0.5, size_t = 0.8)
```

